---
title: "exploratory_data_analysis"
author: "M_Raess"
date: "5/27/2017"
output: pdf_document
---

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Exploratory data analysis

```{r read in data, eval=TRUE, echo=FALSE}

library(tidyverse)
library(ggplot2)

diss_data <- readRDS("diss_data.rds")

tweet_data_ger <- readRDS("tweet_data_ger.rds")
```

## Diss data

```{r summary str, echo=TRUE, eval=TRUE}

#summary(diss_data)

#str(diss_data)

diss_data$alt_zip <- unlist(diss_data$alt_zip)

summary(diss_data)

str(diss_data)

```

## Correlation matrix for all variables

```{r cors, echo=TRUE, message=FALSE}

library(Hmisc)

diss_data_cor <- diss_data %>% select(e, a, c, n, o, time_twitter_min, age, tweet_num, hash_dens, emoji_dens, tt_50) %>% na.omit ## vars need to be completed by imputation...

rcorr(as.matrix(diss_data_cor, type= "pearson")) # creates a correlation matrix

cor <- cor(diss_data_cor)

# Create correlation plots

library(qgraph)
library(corrplot)

#now plot a graph of the correlation matrix

qgraph(cor, shape="circle", posCol="darkgreen", negCol="darkred", layout="groups", vsize=10)

corrplot(cor, method="square")

```

Neg. cor between e and time_twitter_min - maybe not rich get richer but social compensation hypothesis??

### Years on Twitter

```{r years_twitter, echo=TRUE}

ggplot(diss_data) + geom_bar(aes(x = years_twitter, fill = gender), position = "dodge") +
        scale_fill_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender")

```

### Check Twitter how many times

```{r check_twitter, echo=TRUE}

ggplot(diss_data) + geom_bar(aes(x = check_twitter, fill = gender), position = "dodge") +
        scale_fill_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender")

```

### Minutes on Twitter/day

```{r time_twitter_min, echo=TRUE}

range(diss_data$time_twitter_min)

ggplot(diss_data) + geom_histogram(aes(time_twitter_min, ..density..), binwidth = 20) +
        geom_density(aes(x = time_twitter_min, y = ..density..),col = "steelblue", 
                     lwd = 1, fill = "steelblue", alpha = 0.5) +
        stat_function(fun = dnorm, color = "goldenrod", lwd = 1, args = list(mean = mean(diss_data$time_twitter_min), sd = sd(diss_data$time_twitter_min)))

```


### Distribution by gender

```{r gender, echo=TRUE}

library(ggplot2)
source("theme_matt.R")

ggplot(diss_data) + geom_bar(aes(x = gender, fill = function_hash))

ggplot(diss_data) + geom_bar(aes(x = gender, y = ..prop.., group = 1))

ggplot(diss_data) + geom_boxplot(aes(gender, age, fill = gender), notch = TRUE) + 
        geom_hline(mapping = aes(yintercept = mean(age)), col = "red") +
        geom_hline(mapping = aes(yintercept = median(age)), col = "yellow") +
        coord_flip() + theme_minimal() + 
        scale_fill_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender")


ggplot(diss_data) + geom_boxplot(aes(gender, tweet_num))

ggplot(diss_data) + geom_point(aes(age, tweet_num)) + geom_smooth(aes(age, tweet_num), method = "loess")

ggplot(diss_data) + geom_point(aes(age, tt_50, col = gender)) +
        scale_color_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender") +
        ggtitle("Time to 50 tweets/age/gender") +
        geom_smooth(aes(age, tt_50, col = gender), se = FALSE) +
        theme_matt()

ggplot(diss_data) + geom_point(aes(age, hash_dens, col = gender)) +
        scale_color_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender") +
        ggtitle("Hashtag density across age/gender") +
        geom_smooth(aes(age, hash_dens, col = gender), se = FALSE) +
        theme_matt()

ggplot(diss_data, aes(age, emoji_dens, col = gender, shape = gender)) + 
        geom_point(size = 2) +
        scale_color_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender") +
        scale_shape_discrete(name = "Gender") +
        geom_smooth(method = "loess", se = FALSE) +
        ggtitle("Emoji density across age/gender") +
        theme_matt()

library(plotly)

plot <- plot_ly(diss_data, x = ~age, y = ~tweet_num, z = ~hash_dens,
                marker = list(color = ~emoji_dens, showscale = TRUE)) %>% 
        add_markers() %>% 
        layout(scene = list(xaxis = list(title = 'Age'),
                            yaxis = list(title = 'Tweet_num'),
                            zaxis = list(title = 'Hash_dens')),
               annotations = list(text = "Emoji_dens",
                                  xref = "paper",
                                  yref = "paper",
                                  xref = "Age",
                                  yref = "Tweet_num",
                                  showarrow = FALSE
                                  ))

```

Chi-Square for gender and hashtag function

```{r chi-square, echo=TRUE}

library(MASS)

data_sub <- diss_data %>% filter(function_hash == "both" | function_hash == "tag") %>% droplevels()

tbl <- table(data_sub$gender, data_sub$function_hash)

chisq.test(tbl)

```

Gender and hashtag are independent and thus not related in some way...

### Age

```{r age, echo=TRUE}

ggplot(diss_data) + geom_histogram(aes(age, ..density..), col = "lightgrey", binwidth = 20, alpha = 0.4) +
        geom_density(aes(x = age, y = ..density..),col = "steelblue", 
                     lwd = 1, fill = "steelblue", alpha = 0.5) +
        stat_function(fun = dnorm, color = "goldenrod", lwd = 1, args = list(mean = mean(diss_data$age), sd = sd(diss_data$age))) +
        theme_matt()

```


### Relationship

```{r relationship, echo=TRUE}

ggplot(diss_data) + geom_bar(aes(x = relationship, fill = gender), position = "dodge") +
        scale_fill_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender")

```

### Education 1 + 2

```{r edu, echo=TRUE}

ggplot(diss_data) + geom_bar(aes(x = edu, fill = gender), position = "dodge") +
        scale_fill_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender")

ggplot(diss_data) + geom_bar(aes(x = edu2, fill = gender), position = "dodge") +
        scale_fill_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender")

```

### Employ

```{r employ, echo=TRUE}

ggplot(diss_data) + geom_bar(aes(x = employ, fill = gender), position = "dodge") +
        scale_fill_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender")

```

### Check out distributions of tweet_num, hashtag density, and emoji density

```{r densities, echo=TRUE}

library(ggplot2)

ggplot(diss_data) + geom_histogram(aes(tweet_num, ..density..), binwidth = 20) +
        geom_density(aes(x = tweet_num, y = ..density..),col = "steelblue", lwd = 1, 
                     fill = "steelblue", alpha = 0.5) +
        stat_function(fun = dnorm, color = "goldenrod", lwd = 1, args = list(mean = mean(diss_data$tweet_num), sd = sd(diss_data$tweet_num)))


```

This approximates a negative binomial distribution (count data!!!) (maybe poisson...but is more general)

Upon further inspection, part_id25 turned out to be a marketing-only twitter account (based on tweet_num and tweet texts and most frequent hashtag "gratismail"). It was thus removed from the dataset...

```{r subsetI, echo=TRUE}

diss_data <- diss_data %>% filter(!part_id == "25") # reduces part num to 62

saveRDS(diss_data, file = "diss_data.rds")

tweet_data_ger <- tweet_data_ger %>% filter(!part_id == "25") # reduces tweets to 19772

saveRDS(tweet_data_ger, file = "tweet_data_ger.rds")

ggplot(diss_data) + geom_histogram(aes(tweet_num, ..density..), binwidth = 20) +
        geom_density(aes(x = tweet_num, y = ..density..),col = "steelblue", lwd = 1, 
                     fill = "steelblue", alpha = 0.5) +
        stat_function(fun = dnorm, color = "goldenrod", lwd = 1, args = list(mean = mean(diss_data$tweet_num), sd = sd(diss_data$tweet_num)))

```



```{r densitiesIV, echo=TRUE, message=FALSE}

library(ggplot2)

ggplot(diss_data) + geom_histogram(aes(emoji_dens, ..density..), binwidth = 20) +
        geom_density(aes(x = emoji_dens, y = ..density..),col = "steelblue", lwd = 1, 
                     fill = "steelblue", alpha = 0.5) +
        stat_function(fun = dnorm, color = "goldenrod", lwd = 1, args = list(mean = mean(diss_data$emoji_dens), sd = sd(diss_data$emoji_dens)))

```

### Check out dist of personality scores

```{r personality, echo=TRUE, message=FALSE}

library(tidyverse)

diss_data_gather <- diss_data %>% gather(`e`, `a`, `c`, `n`, `o`, key = "p_type", value = "bfi10_score") %>% arrange(part_id)

ggplot(diss_data_gather) + geom_boxplot(aes(p_type, bfi10_score, fill = gender)) + 
        stat_summary(mapping = aes(p_type, bfi10_score, fill = gender), 
                     dfun.y = mean, colour="orange", geom="point", shape=16, size=2, 
                     position = position_dodge(width = 0.75)) +
        theme_minimal() + 
        scale_fill_manual(values = c(female = "tomato", male = "steelblue"), name = "Gender")

ggplot(diss_data) + geom_point(aes(e, tweet_num))

ggplot(diss_data) + geom_point(aes(a, tweet_num))

ggplot(diss_data) + geom_point(aes(c, tweet_num))

ggplot(diss_data) + geom_point(aes(n, tweet_num))

ggplot(diss_data) + geom_point(aes(o, tweet_num))

## tweet_num per part is count data - poisson...

```


